---
title: "Generalized Additive Models for Location, Scale, and Shape (GAMLSS)"
author: "Joshua Edefo"
date: "2025-01-28"
email: "edefojoshua2000@yahoo.com"
output: github_document
---
GAMLSS is a statistical framework that has great flexibility and power. Some benefits include flexibility in distribution, modelling resulting into multiple parameters, also works  well with non-linear relationships of variables and handles heterogeneity. However, it also comes with some disadvantages, such as complexity, interpretability and software availability 

It is used to model the effect of number of seizures episodes (n_epil), medication adherence (adh), and number of medications taken (n_med) on quality of life (qol) of epilepsy patients


Libraries
```{r a, message=FALSE}
library(gamlss)
library(usethis)
```

Data and preparation of data


```{r b}
data <- read.csv("C:/Users/joe62/OneDrive - Aberystwyth University/Apps/Desktop/Destop Folder/R code/ep.csv")

##Checking the structure
str(data)
summary(data)

## Remove observations with missing values

data = na.omit(data)

```

Fitting the GAMLSS model and model summary
```{r c}
model <- gamlss(
  qol ~ n_epil + adh + n_med,
  data = data,
  family = BCT
)

summary(model)

```

Summary of results
Mu (Location) Coefficients:
  Intercept: 2.26117 (highly significant, p < 2e-16).
n_epil: 0.28306 (highly significant, p < 6.28e-09).
adh: -0.08966 (highly significant, p < 1.50e-05).
n_med: 0.10813 (not significant, p = 0.265).
Sigma (Scale) Coefficient:
  Intercept: -1.20974 (highly significant, p < 2e-16).
Nu (Shape) Coefficient:
  Intercept: 0.05458 (not significant, p = 0.799).
Tau (Shape) Coefficient:
  Intercept: 34.19 (highly significant, p < 2e-16).
  
  
  session information

```{r d}
sessionInfo()
```

